### 2021-02-16 paper/natastron/Publication/bblmethods.tex
paper done

\bibitem{huber+2013a}
\bibinfo{author}{Huber, D.} \emph{et~al.}
\newblock \bibinfo{title}{Stellar {{Spin}}-{{Orbit Misalignment}} in a
	{{Multiplanet System}}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{342}},
\bibinfo{pages}{331} (\bibinfo{year}{2013}).

@@

\bibitem{tassoul1980}
\bibinfo{author}{Tassoul, M.}
\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
	pulsations}.
\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).

@@

\bibitem{chaplin+2011}
\bibinfo{author}{Chaplin, W.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Ensemble {{Asteroseismology}} of {{Solar}}-{{Type
			Stars}} with the {{NASA Kepler Mission}}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
\bibinfo{pages}{213} (\bibinfo{year}{2011}).

@@

\bibitem{foreman-mackey2016}
\bibinfo{author}{{Foreman-Mackey}, D.}
\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
\textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).

\end{thebibliography}

>>>>

\bibitem{huber+2013a}
\bibinfo{author}{{Barnes}, S.~A.}
\newblock \bibinfo{title}{{A Simple Nonlinear Model for the Rotation of
  Main-sequence Cool Stars. I. Introduction, Implications for Gyrochronology,
  and Color-Period Diagrams}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
  \textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222--234}
  (\bibinfo{year}{2010}).

@@

\bibitem{tassoul1980}
\bibinfo{author}{{Tassoul}, M.}
\newblock \bibinfo{title}{{Asymptotic approximations for stellar nonradial
  pulsations.}}
\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
  \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469--490}
  (\bibinfo{year}{1980}).

@@

\bibitem{chaplin+2011}
\bibinfo{author}{{Chaplin}, W.~J.} \emph{et~al.}
\newblock \bibinfo{title}{{Ensemble Asteroseismology of Solar-Type Stars with
  the NASA Kepler Mission}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{332}},
  \bibinfo{pages}{213} (\bibinfo{year}{2011}).
\newblock \eprint{1109.4723}.

@@

\bibitem{foreman-mackey2016}
\bibinfo{author}{{Foreman-Mackey}, D.}
\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
  \textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).
\end{thebibliography}
